\subsection{Swarm Fusion optical flow}

Fusion Move was first introduced by Lempitsky et al.~\cite{viktor} to
solve the optical flow problem. \chen{Again, I think Lempitsky's work doesn't
  aim at the optical flow problem.}
%Optical flow was the problem, in which the Fusion Move method was first
%introduced by Lempitsky et al.~\cite{viktor}.
We copy their problem setting and proposal generation schemes for
our second problem.
  We use images from the Middlebury optical flow
benchmark~\cite{middlebury_optical_flow}.

\chen{I made a mistake that I didn't use the same proposal generation schemes
  with their work. Instead of HS algorithm, I use Farneback algorithm to generate proposals because it is right there in OpenCV. I also add a bunch of other less useful proposals to have more proposal generation schemes for more clear comparisons..
  I think we could write in short as follows.}

\chen{We share similar proposal generation schemes with Lempitsky et al ~\cite{viktor}, but instead of the HS algorithm, we use more recent Farneback algorithm and changes its pyramid levels from 1 to 5 and use different polyN {3, 5, 7}. Besides the clustering idea, ~\cite{viktor} also suggests to use more proposals generation schemes based on the current solution. We add three simple proposal generation schemes to better explore the power of our parallel pipeline. In \textit{shift proposal}, the flow field in the current solution is shifted in either x direction or y direction for either 1, 2 or 3 pixels. In \textit{stagger proposal}, the flow field is shifted by a vector randomly drawed from a Gaussian distribution. In \textit{disturb proposal}, each flow value in the field is indenpendantly shifted by a vector randomly drawed from a Gaussian distribution.}

\mysubsubsection{Competing methods}

\noindent Fusion Move method in Lempitsky's paper is the first natural
contender. While they did not consider parallel implementation, it is
straightforward to combine the idea of Parallel Alpha Expansion and
Fusion Move. Therefore, the second competing method is ``Parallel Fusion
Move''(PFM), which is equivalent to Parallel Alpha Expansion with constant
label solutions replaced by solution proposals.
%each thread repeats generating
%a solution proposal and fusing it to the current solution. Solutions
%from all the results are sequentially fused to obtain the final solution
%as in the Parallel Alpha-Expansion method.
%
One problem of PFM is that infinite number of solution proposals can be
generated in their algorithm, and we do not know when to stop and
perform the final sequential fusion (See Parallel Alpha Expansion
architecture in Fig.~\ref{fig:model}). In our experiments, we manually
picked time limits to initiate the final fusion to make the comparisons
fair.
%In Fig.~\ref{fig:model}, this computational framework corresponds to
%``parallel alpha-expansion'' with the label solutions replaced by
%solution proposals.
%
The last contender is the mix of the Hierarchical Fusion and the Fusion
Move methods, dubbed ``Hierarchical Fusion Method''(HFM), where they
start from solution proposals as opposed to constant labels. One problem
of HFM is that the number of necessary solution proposals is unknown
before solving the problem, and the tree of labels cannot be defined. In
our experiments, we have manually picked a good number (X \yasu{how many
  Hang?}) \chen{77 proposals in total (We first generate 11 proposals using LK and Farneback algorithms which do not require current solution and generate other proposals based on these initial proposals).} to generate proposals.
%
The fusions are binary in these methods and we have used QPBO.

\mysubsubsection{Swarm fusion architectures}

\noindent
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} (SF-SS, SF-MF, SF)
have been evaluated against the competing methods. The same
configurations as in the stereo problem have been used for optical flow,
that is, $\alpha=2$ ($\beta=0$) for SF-SS, the iteration of
($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) for SF-MF, and
($\alpha=1, \beta=1$) \chen{($\alpha=2, \beta=0$) and ($\alpha=0, \beta=2$)} for SF.
%
Note that we have used the same set of proposal generation schemes as
the competing methods. We have used TRW-S for multi-way fusion and QPBO
for binary fusion. \chen{Just for clarification, I always use TRW-S and just set the number of
  labels to be 2. It is the same with QPBO as mentioned by Pushmeet.}
%, while our fusions are multi-way, for which we have used TRW-S.
%
% The full swarm fusion model (at the bottom right in
% Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
% method. We will also try the other two Swarm fusion variants in
% Fig.~\ref{fig:model} with restrictions.

2 k-way 1 solution sharing. \chen{?}
